PANCHANGE_analysis

### 2020-11-10 PANCHANGE_analysis.Rmd
Knitted edgi preprocessing script

# GAD baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad model0a absolute whole sample}
# Regression coefficients
gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0a_estimates)
gad_baseline_model0a_estimates

# Regression diagnostic statistics
gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0a_reg_stats)
gad_baseline_model0a_reg_stats
```

>>>>

# GAD baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted

#SB Hashing out this chunk of code as it is not included in our final analysis and is currently breaking the code.
```{r gad model0a absolute whole sample}
# Regression coefficients
#gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
 #                                                data_set = "dat")
#kable(gad_baseline_model0a_estimates)
#gad_baseline_model0a_estimates

# Regression diagnostic statistics
#gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
  #                                               data_set = "dat")
#kable(gad_baseline_model0a_reg_stats)
#gad_baseline_model0a_reg_stats
```
